---
title: "Introduction to varselect"
author: "Shahad"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to VarSelect}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

varselect provides comprehensive variable selection with an intuitive pipeline architecture.


## Quick Example

```{r eval=FALSE}
data(mtcars)

# Simple usage
pipeline <- varselect(mtcars, "mpg") + fullselection()

# View results
pipeline@final_vars
pipeline@performance
```

## Advanced Example

```{r eval=FALSE}
# Custom pipeline
pipeline <- varselect(mtcars, "mpg") +
  validate(exclude = c("cyl")) +
  significance(alpha = 0.05, correction = "fdr") +
  refine(vif_threshold = 10) +
  selection(method = "backward", cv_folds = 10) +
  prediction() +
  visualize(type = "importance") +
  train()
```

## Key Features

### 1. Multiple Selection Methods
- Backward (default)
- Forward
- Stepwise
- Hybrid

### 2. Advanced Metrics
- Mallow's Cp
- Spearman/Kendall correlations
- AUC, F1, MCC for classification
- R², Adjusted R², RMSE, MAE for regression

### 3. Statistical Rigor
- FDR correction
- VIF analysis
- Condition numbers
- Stratified CV

## More Information

See `?varselect` for full documentation.
